\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-08-19 NAR_DRAFT.tex
small fixes

\usepackage{NAR-natbib}
\bibliographystyle{unsrtnat}
\usepackage{color}
\usepackage{xfrac}
\newcommand{\rngcomment}[1]{{\color{red}RNG: #1}}
\newcommand{\bkmcomment}[1]{{\color{blue}BKM: #1}}
\newcommand{\batcave}{BATCAVE }
% Enter dates of publication
\copyrightyear{2008}
\pubdate{31 July 2009}
\pubyear{2009}
\jvolume{37}
\jissue{12}

@@

Assuming that the identity of the alternate allele and its allele frequency are independent of each other, and $\nu$ is uniformly distributed (i.e. $\mathrm{p}(\nu) = 1$), we can rewrite equation \ref{eqn:1} as
\begin{equation}
  \label{eqn:2}
$$
  P(m,\nu) = p(m) \cdot \prod_{i=1}^{\mathrm{d}} \textrm{f}_{m,\nu}(x_i).
$$
\end{equation}
Here we show how \batcave can be used to provide a tumor and site-specific estimate of the prior probability of mutation $p(m)$.

@@

	We use the Integrated Calibration Index to quantify the difference between MuTect and the Calibrated model \cite{Austin2019}.
	Briefly, a loess-smoothed regression is fit by regressing the binary (T/F) variant classification against the reported posterior probability of a true variant for both MuTect and the Calibrated model (Figure \ref{NAR-wes_fig} \textbf{e}).
	Plotting the smoothed regression predictions against the actual predictions would result in a diagonal line, and the Integrated Calibration Index is the average distance between the loess fit and a diagonal line.

@@

\bibliography{caller_paper}
\clearpage
\onecolumn
\section{Supplememtary Figures}

>>>>

\usepackage{NAR-natbib}
\bibliographystyle{unsrtnat}
\usepackage{color}
\usepackage{xfrac}
\newcommand{\rngcomment}[1]{{\color{red}RNG: #1}}
\newcommand{\bkmcomment}[1]{{\color{blue}BKM: #1}}
\newcommand{\batcave}{BATCAVE }
\newcommand{\beginsupplement}{%
        \setcounter{table}{0}
        \renewcommand{\thetable}{S\arabic{table}}%
        \setcounter{figure}{0}
        \renewcommand{\thefigure}{S\arabic{figure}}%
     }
% Enter dates of publication
\copyrightyear{2008}
\pubdate{31 July 2009}
\pubyear{2009}
\jvolume{37}
\jissue{12}

@@

Assuming that the identity of the alternate allele and its allele frequency are independent of each other, and $\nu$ is uniformly distributed (i.e. $\mathrm{p}(\nu) = 1$), we can rewrite equation \ref{eqn:1} as
\begin{equation}
  \label{eqn:2}
$$
  P(m,\nu) = p(m) \cdot \prod_{i=1}^{\mathrm{d}} \textrm{f}_{m,\nu}(x_i).
$$
\end{equation}
Here we show how \batcave can be used to provide a tumor and site-specific estimate of the prior probability of mutation $\mathrm{p}(m)$.

@@

	We use the Integrated Calibration Index to quantify the difference between MuTect and \batcave \cite{Austin2019}.
	Briefly, a loess-smoothed regression is fit by regressing the binary (T/F) variant classification against the reported posterior probability of a true variant for both MuTect and the Calibrated model (Figure \ref{NAR-wes_fig} \textbf{e}).
	Plotting the smoothed regression predictions against the actual predictions would result in a diagonal line, and the Integrated Calibration Index is the average distance between the loess fit and a diagonal line.

@@

\bibliography{caller_paper}
\clearpage
\onecolumn
\beginsupplement
\section{Supplememtary Figures}
